\documentclass[letter,10pt]{article}
\usepackage{TLCresume}
\begin{document}

%====================
% EXPERIENCE A
%====================
\subsection{{GitHub Extern '22 \hfill Feb 2022 --- Present}}
\subtext{Suborbital}
\begin{zitemize}
\item Tech Stack -- WebAssembly, Golang, Swift, Rust, Atmo, Reactr, Compile.
\item The main work involves working on a CLI tool named Subo built in Golang.
\end{zitemize}

%====================
% EXPERIENCE B
%====================
\subsection{{SDE Intern \hfill Oct 2021 --- Mar 2022}}
\subtext{Brane Enterprises \hfill}
\begin{zitemize}
\item Tech Stack -- Android Studio, Flutter, Dart.
\item The main work involved working on an app based on multiple micro-services and cloud-computing architecture.
\end{zitemize}

%====================
% EXPERIENCE C
%====================
\subsection{{SDE Intern \hfill Sep 2021 --- Dec 2021}}
\subtext{Surya Softwares \hfill}
\begin{zitemize}
\item Tech Stack -- Golang, Postman.
\item The main work involved working on Surya's RPC server and its CLI tool to support automatic generation of Postman collections.
\end{zitemize}

%====================
% EXPERIENCE D
%====================
\subsection{{SDE Intern \hfill Jul 2021 --- Aug 2021}}
\subtext{Surya Softwares \hfill}
\begin{zitemize}
\item Tech Stack -- Rust, OracleSQL, MicrosoftSQL, PostgresSQL.
\item The main work involved development of Rust libraries to implement the functions of various RDBMS in Rust.
\end{zitemize}

%====================
% EXPERIENCE E
%====================
\subsection{{UI/UX Designer \hfill May 2021 --- Jul 2021}}
\subtext{Seegate Corporation \hfill}
\begin{zitemize}
\item Softwares -- Adobe Illustrator, Adobe XD.
\item The main work involved creation and handling of the company website's UI/UX.
\end{zitemize}

%====================
% EXPERIENCE F
%====================
\subsection{{Graphic Designer \hfill Jan 2021 --- May 2021}}
\subtext{Neurotech Design \hfill}
\begin{zitemize}
\item Softwares -- Adobe Illustrator, Adobe XD, Figma.
\item The main work involved creation and handling of the company's graphics(website and social media).
\end{zitemize}

%====================
% EXPERIENCE G
%====================
\subsection{{Graphic Designer \hfill Nov 2020 --- Feb 2021}}
\subtext{Shubhchintak Technology \hfill}
\begin{zitemize}
\item Softwares -- Adobe Illustrator, Adobe XD.
\item The main work involved creation and handling of the company's graphics(website and social media).
\end{zitemize}

%====================
% EXPERIENCE H
%====================
\subsection{{Tech Blogger \hfill Sep 2020 --- Oct 2020}}
\subtext{Shubhchintak Technology \hfill}
\begin{zitemize}
\item The main work involved writing tech-based blogs for the company's website.
\end{zitemize}

%====================
% EXPERIENCE I
%====================
\subsection{{Tech Blogger \hfill Jul 2020 --- Aug 2020}}
\subtext{SOLVE Foundation \hfill}
\begin{zitemize}
\item The main work involved writing tech-based blogs for an IITD based startup under SOLVE.
\end{zitemize}

\end{document}